\documentclass[10pt,letterpaper]{article}
\usepackage{cv}

\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{url}
\hypersetup{
    colorlinks=true,
    linkcolor=NavyBlue,
    urlcolor=NavyBlue,
    citecolor=NavyBlue}
\urlstyle{same}



\begin{document}
\begin{center}
{\LARGE \textbf{T. Scott Trinkle}}\\
\end{center}
\vspace{-1em}

\subsection*{Biographical Information}
\begin{itemize}[noitemsep]
\item[] \itab{Location:} \tab{Atlanta, GA}
\item[] \itab{Email:} \tab{scott\_trinkle@waters.com}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Current position
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Experience}
\begin{benumerate}{2}
\item
  \textbf{Senior Data Scientist} \hfill January 2022--\\
  Waters Corporation\\
  Milford, MA

\item
  \textbf{Machine Learning Intern} \hfill June 2021--September 2021\\
  Waters Corporation\\
  Milford, MA
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Education}
\begin{benumerate}{2}
\item
  \textbf{University of Chicago} \hfill December 2021\\
  Ph.D., Medical Physics\\
  Thesis: ``\href{https://www.proquest.com/openview/5ce6c9b022b339d81e3cd47cc0cdf8fa/1?pq-origsite=gscholar&cbl=18750&diss=y}{Multi-modal validation of MR microstructure imaging in the mouse brain}''\\
  Advisor: Dr. Patrick La Rivi\`ere \\
  GPA: 3.92/4.00\\
\item
  \textbf{University of Florida} \hfill May 2016\\
  B.S., Nuclear and Radiological Science, \textit{summa cum laude}\\
  Thesis: ``Development of a Novel Tissue-Equivalent Physical Phantom for Experimental Validation
  of CT Dosimetry under Tube Current Modulation''\\ 
  GPA: 3.92/4.00\\
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Original Peer-Reviewed Journal Articles}
\begin{benumerate}{4}
\item \textbf{Trinkle, S.}, Wildenberg, G., Kasthuri, N., La Rivière, P.,
  Foxley, S. ``Model-free analysis in the spectral domain of postmortem mouse
  brain EPSI reveals inconsistencies with model-based analyses of the free
  induction decay,'' \textit{BioRxiv}, 2022,
  2022.02.24.481824. \href{https://doi.org/10.1101/2022.02.24.481824}{https://doi.org/10.1101/2022.02.24.481824}.
\item \textbf{Trinkle, S.}, Foxley, S., Wildenberg, G., Kasthuri, N., La
  Rivi\`ere, P., ``The role of spatial embedding in mouse brain networks
  constructed from diffusion tractography and tracer injections,''
  \textit{NeuroImage}, vol. 244, p. 118576, 2021, ISSN: 1053--8119. DOI:
  \href{https://doi.org/10.1016/j.neuroimage.2021.118576}{https://doi.org/10.1016/j.neuroimage.2021.118576}.
\item Foxley, S., Sampathkumar, V., De Andrade, V., \textbf{Trinkle, S.},
  Sorokina, A., Norwood, K., LaRivi\`ere, P., Kasthuri, N., ``Multi-modal
  imaging of a single mouse brain over five orders of magnitude of resolution,''
  \textit{NeuroImage}, vol. 238, p. 118250, 2021, ISSN: 1053--8119. DOI:
  \href{https://doi.org/10.1016/j.neuroimage.2021.118250}{https://doi.org/10.1016/j.neuroimage.2021.118250}.
\item \textbf{Trinkle, S.}, Foxley, S., Kasthuri, N., La Rivi\`ere, P.,
  ``Synchrotron X-ray micro-CT as a validation dataset for diffusion MRI in
  whole mouse brain,'' \textit{Magnetic Resonance in Medicine}, vol. 86, no. 2,
  pp. 1067--1076, 2021. DOI:
  \href{https://doi.org/10.1002/mrm.28776}{https://doi.org/10.1002/mrm.28776}.
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstracts/Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Abstracts/Presentations}
\begin{benumerate}{17}

\item{``MSI Quantify: A micro-app for the automated processing of \hfill 6/2023\\ quantitative mass spectrometry data.''\\
    \textbf{Trinkle S}, Jones E, Towers M, Chapman R, Claude E.\\
    71st ASMS Conference on Mass Spectrometry and Allied Topics, Houston, TX.\\
    Poster.}
  
\item{``Automated visualization, exploration and material segmentation of \hfill 6/2023\\ ion-mobility mass spectrometry imaging data.''\\
    \textbf{Trinkle S}, Gangal A, Mather J, Shrestha B, Chapman R.\\
    71st ASMS Conference on Mass Spectrometry and Allied Topics, Houston, TX.\\
    Poster.}
  
\item{``An automated workflow for combining, aligning, exploring, and \hfill 6/2023\\ visualizing 3D MS imaging data.''\\
    Chapman R, \textbf{Trinkle S}, Jones E.\\
    71st ASMS Conference on Mass Spectrometry and Allied Topics, Houston, TX.\\
    Poster.}
  
\item{``An automated computational pipeline for retention time alignment \hfill 6/2023\\ across LC systems.''\\
    Reah I, \textbf{Trinkle S}, Marchand R, Preston C, Morns I, Chapman R, Fitch P.\\
    71st ASMS Conference on Mass Spectrometry and Allied Topics, Houston, TX.\\
    Poster.}
  
\item{``DESI imaging at the cellular level through the application \hfill 6/2023\\ of nano-flow and multi-focus approaches.''\\
    Jones E, Hoyes E, \textbf{Trinkle S}, Chapman R.\\
    71st ASMS Conference on Mass Spectrometry and Allied Topics, Houston, TX.\\
    17 minute talk.}
  
\item{``A machine learning-based pipeline for background classification and \hfill 9/2022\\ data reduction in mass spectrometry imaging.''\\
    \textbf{Trinkle S}, Jones E, Chapman R.\\
    42nd BMSS Annual Meeting, Manchester, UK.\\
    Poster.}
  
\item{``MSI-Segmentation: a web-based micro-app for automated exploration \hfill 9/2022\\ and material segmentation of MS imaging data.''\\
    \textbf{Trinkle S}, Jones E, Chapman R.\\
    42nd BMSS Annual Meeting, Manchester, UK.\\
    Poster.}

\item{``MSI-Segmentation: a micro-app for automated exploration \hfill 8/2022\\ and material segmentation of mass spectrometry imaging data.''\\
    \textbf{Trinkle S}, Jones E, Chapman R.\\
    Imaging Mass Spectrometry Society Summer Workshop 2022, Baltimore, MD.\\
    Poster.}
  
\item{``A machine learning-based pipeline for background classification and \hfill 6/2022\\ data reduction in mass spectrometry imaging.''\\
    \textbf{Trinkle S}, Jones E, Chapman R.\\
    70th ASMS Conference on Mass Spectrometry and Allied Topics, Minneapolis, MN.\\
    Poster.}
  
\item{``MSI-Segmentation: a web-based micro-app for automated exploration \hfill 6/2022\\ and material segmentation of MS imaging data.''\\
    \textbf{Trinkle S}, Jones E, Chapman R.\\
    70th ASMS Conference on Mass Spectrometry and Allied Topics, Minneapolis, MN.\\
    Poster.}
  
\item{``Rapid development of predictive models and software tools for IMS research \hfill 6/2022\\ enabled by Saas and Low Code Computing.''\\
    Ianchis V, Gioioso M, Colley P, Vissers J, Kharit B, \textbf{Trinkle S}, Chapman R.\\
    70th ASMS Conference on Mass Spectrometry and Allied Topics, Minneapolis, MN.\\
    Poster.}
  
\item{``Synchrotron microCT tractography connectomics: comparison with \hfill 8/2020\\ diffusion MRI and neural tracer injections.''\\
    \textbf{Trinkle S}, Foxley S, Kasthuri N, La Rivière P.\\
    ISMRM 28$^{\text{th}}$ Annual Meeting, Paris, France.\\
    \textit{Virtual presentation due to COVID-19 pandemic.}\\
    \textit{Received Magna Cum Laude Merit Award.}\\
    12 minute talk.}

\item{``X-ray microcomputed tomography as a natively isotropic, nondestructive, \hfill 5/2019\\
    3D validation dataset for diffusion MRI.''\\
    \textbf{Trinkle S}, Foxley S, Kasthuri N, La Rivière P.\\
    ISMRM 27$^{\text{th}}$ Annual Meeting, Montr\'eal, QC, Canada.\\
    \textit{Received Magna Cum Laude Merit Award.}\\
    12 minute talk.}
  
\item{``Towards whole-brain validation of diffusion MRI fiber-orientation \hfill 6/2018\\
    distributions with x-ray microcomputed tomography.''\\
    \textbf{Trinkle S}, Foxley S, Kasthuri N, La Rivière P.\\
    Gordon Research Conference on Image Science, Easton, MA. \\
    Poster.}

\item{``High-resolution mapping of optical path difference using \hfill 1/2018\\
    orientation-independent differential interference contrast microscopy'' \\
    Shribak M, Mehta S, Zuckerburg C, Rhines T, \textbf{Trinkle S}, La Rivi\`ere P\\
    SPIE Photonics West Conference, San Francisco, CA. \\
    Invited Talk (cancelled due to scheduling conflict).}
  
\item{``Quantitative analysis of temporal subtraction chest radiographs.''\hfill 8/2017\\
    \textbf{Trinkle S}, Engelmann R, Macmahon H, Armato S. \\
    AAPM Annual Meeting, Denver, CO. \\
    ePoster.}

\item{``Development of a Novel Tissue-Equivalent Physical Phantom for \hfill 3/2016\\
    Experimental Validation of CT Dosimetry under TCM'' \\
    \textbf{Trinkle S}, Stepusin E, Olguin E, Bolch W.\\
    UF Undergraduate research symposium, Gainesville, FL. \\
    Poster.}

\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Miscellaneous Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \mysubsection{Miscellaneous Other Presentations}
% \begin{benumerate}{6}

% \item {``I'll show you the life of the mind! Single-neuronal predictions of
%     others' beliefs'' \hfill 2/2021\\
%     Graduate Program in Medical Physics Journal Club. \\
%     30 minute talk.
%   }
% \item{``Multi-modal validation of diffusion MRI tractography'' \hfill 5/2020\\
%     Graduate Program in Medical Physics Colloquium Series, Chicago, IL.\\
%     60 minute talk.}

% \item{``Head for the hills! Estimating population risk to rising sea levels'' \hfill 3/2020\\
%     Graduate Program in Medical Physics Journal Club. \\
%     30 minute talk.}

% \item{``Does your vote matter? Wealth and influence in American democracy.'' \hfill 1/2019\\
%     Graduate Program in Medical Physics Journal Club. \\
%     30 minute talk.}

% \item{``Moderating risky gambling behavior'' \hfill 3/2018\\
%     Graduate Program in Medical Physics Journal Club. \\
%     30 minute talk.}
  
% \item{``Charged Particle Emission Tomography'' \hfill 4/2017\\
%     Graduate Program in Medical Physics Journal Club. \\
%     30 minute talk.}

% \end{benumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Research Experience}
\begin{benumerate}{5}
\item
  {\textbf{La Rivi\`ere Lab}, University of Chicago} \hfill 7/2017--\\
  Advisor: Dr. Patrick La Rivi\`ere\\
  Topics: Multi-modal microstructure imaging validation
\item
  {\textbf{Pan Lab}, University of Chicago} \hfill 3/2017--6/2017\\
  Advisor: Dr. Xiaochuan Pan\\
  Topics: Dual-energy CT
\item
  {\textbf{Center for EPR Imaging in Vivo Physiology}, \\
    University of Chicago} \hfill 1/2017--3/2017\\
  Advisor: Dr. Howard Halpern\\
  Topics: EPR Imaging, dose profile validation
\item
  {\textbf{Armato Lab}, University of Chicago} \hfill 9/2016--12/2016\\
  Advisor: Dr. Sam Armato\\
  Topics: Computer-aided diagnosis, temporal subtraction radiography
\item
  {\textbf{Advanced Laboratory for Radiation Dosimetry Studies}, \\
    University of Florida} \hfill 1/2013--5/2016\\
  Advisor: Dr. Wesley Bolch\\
  Topics: Physical phantom construction, computational dosimetry
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Current Funding Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Funding Awards}
\begin{benumerate}{1}
\item
  Principal Investigator: T. Scott Trinkle\\
  Title: \textit{A novel multi-modal, multi-scale imaging pipeline for the
    validation of diffusion MRI of the brain.}\\
  Source: NIH National Research Service Award (F31)\\
  Project period: 7/1/2019--12/31/2021\\
  Total direct costs: \$120,979\\
  Project role: Contact PI (100\% effort)
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching activity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Teaching and supervision activity}
\begin{benumerate}{6}

\item
  \textbf{Internship supervisor} \hfill 2023\\
  Akshay Khanna\\
  Topic: Lab methods predictor and analytics platform
\item
  \textbf{Internship supervisor} \hfill 2022--2023\\
  Ayushe Gangal\\
  Topic: Ion-mobility mass spectrometry imaging, multi-modal registration
\item
  \textbf{Introduction to Medical Physics}, University of Chicago \hfill 2020\\
  Teaching Assistant\\
  Topics: Medical imaging, Image Processing, Radiation therapy\\
  Rating: 5.0/5.0 from 12 students\\
  Received 4 nominations for Iguana Award for Teaching Assistants
\item
  \textbf{Undergraduate independent study supervisor} \hfill 2019--2020\\
  Chineze Egwudo\\
  Topic: Tractography parameter optimization
  
\item
  \textbf{Medical Imaging 1}, University of Chicago \hfill 2018\\
  Teaching Assistant\\
  Topics: X-ray imaging, MRI, image restoration\\
  Rating: 5.0/5.0 from 4 students
\item
  \textbf{Mathematics For Medical Physics}, University of Chicago \hfill 2017\\
  Teaching Assistant\\
  Topics: Linear systems theory, stochastic processes, image reconstruction\\
  Rating: 4.8/5.0 from 6 students
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Courses
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Relevant coursework}
\begin{benumerate}{7}

\item
  \textbf{Graph Algorithms and Machine Learning}, Massachusetts Institute of Technology Short Programs \hfill 2023\\
  
\item
  \textbf{Advanced Reinforcement Learning}, Massachusetts Institute of Technology Short Programs \hfill 2023\\
  
\item
  \textbf{Reinforcement Learning}, Massachusetts Institute of Technology Short Programs \hfill 2023\\
  
\item
  \textbf{Applied Data Science Program}, Massachusetts Institute of Technology Short Programs \hfill 2022\\
  Topics: Data visualization, deep learning, recommendation systems, time series analysis
  
\item
  \textbf{Machine Learning for Healthcare}, Massachusetts Institute of Technology Short Programs \hfill 2022\\
  Topics: Risk stratification, clinical NLP, treatment selection, causal inference, survival modeling

\item  
  \textbf{Introduction to Machine Learning}, Toyota Institute of Technology \hfill 2019\\
  Topics: Experimental design, regression, feature selection, SVM, random forests, gradient boosting, deep learning, CNN

\item
  \textbf{Mathematics for Medical Physics}, University of Chicago \hfill 2016\\
  Topics: Optimization, stochastic processes, estimation theory, ROC analysis, linear algebra, non-Gaussian noise models

\end{benumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership Roles
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Leadership Roles}
\begin{benumerate}{1}
\item
  \textbf{Student Co-President}\\
  Graduate Program in Medical Physics, University of Chicago \hfill 2018--2019
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Awards and Honors}
\begin{mybenumerate}{14}
\item \itab{Waters Global Hackathon Most Innovative, Honorable Mention Award}\rtab{-}\hfill{2022}
\item \itab{UChicago Graduate Program in Medical Physics Best Thesis Award}\rtab{\$500}\hfill{2022}
\item \itab{Figure chosen as \href{https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28817}{August issue cover} for}\rtab{-}\hfill{2021}\\
Magnetic Resonance in Medicine
\item \itab{Magna Cum Laude oral session award, ISMRM,}\rtab{-}\hfill{2020} \\
  ``Synchrotron microCT tractography connectomics: \\ comparison with diffusion
  MRI and neural tracer injections''
\item \itab{Magna Cum Laude oral session award, ISMRM,}\rtab{-}\hfill{2019} \\
    ``X-ray microcomputed tomography as a natively isotropic, \\ nondestructive, 3D
    validation dataset for diffusion MRI.''
\item \itab{ISMRM Trainee Stipend}\rtab{\$565}\hfill{2019}
\item \itab{University Scholars Program Award}\rtab{\$1750}\hfill{2016}
\item \itab{N.L. Griesheimer Memorial Scholarship Recipient}\rtab{\$300}\hfill{2015}
\item \itab{Roberto Pagano Memorial Scholarship Recipient}\rtab{\$2000}\hfill{2015}
\item \itab{Bryan Scholarship Recipient}\rtab{\$1000}\hfill{2015}
\item \itab{Anderson Scholar Award}\rtab{-}\hfill{2014}
\item \itab{Wunsch Scholarship Recipient}\rtab{\$1000}\hfill{2014}
\item \itab{Jacobs Scholarship Recipient}\rtab{\$225}\hfill{2013}
\item \itab{Rice Family Scholarship Recipient}\rtab{\$325}\hfill{2013}  
\end{mybenumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Associations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Professional Associations}
\begin{benumerate}{6}
\item \itab{The American Society for Mass Spectrometry (ASMS)} \hfill{2022--}
\item \itab{The International Society for Magnetic Resonance in Medicine (ISMRM)} \hfill{2018--2021}
\item \itab{The International Society for Optics and Photonics (SPIE)}  \hfill{2017--2021}
\item \itab{The American Association of Physicists in Medicine (AAPM)} \hfill{2016--2018}
\item \itab{Health Physics Society (HPS)} \hfill{2015--2016}
\item \itab{American Nuclear Society (ANS)} \hfill{2012--2016}
\end{benumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Computing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysubsection{Computing}
\begin{itemize}[noitemsep]
\item[]
\item[] \itab{\textbf{Top Language:}} \mtab{Python}
\item[] \itab{\textbf{Competent:}} \mtab{MATLAB, Bash}
\item[] \itab{\textbf{Familiar:}} \mtab{SQL, R, \CPP, html}
\item[] \itab{\textbf{Visualization:}} \mtab{Matplotlib, Bokeh, Photoshop, ImageJ}
\item[] \itab{\textbf{Machine learning:}} \mtab{Scikit-learn, Keras, PyTorch, TensorFlow}
\item[] \itab{\textbf{Other tools:}} \mtab{GNU Emacs, \LaTeX, git, Docker, AWS}
\end{itemize}

\end{document}